---
title: "Week 9"
subtitle: "Midterm review"
editor:
  mode: source
format:
  revealjs: 
    output-file: w9-slides.html
    theme: ["simple", "slide_styles/slide-styles.scss"]
    smaller: true
    # navigation-mode: vertical
    slide-number: c/t
    chalkboard: 
      buttons: true
    preview-links: auto
    auto-stretch: false
    transition: fade
    transition-speed: slow
    scrollable: true
    logo: /media/5126-header.png
    css: ["default", "slide_styles/slide-styles.css", "slide_styles/slide-styles.scss"]
---
```{r defaults, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE)
```

```{r setup, include = FALSE, echo = FALSE}
# Check gganimate wiki for more plot examples
pacman::p_load(tidyverse,
               gganimate,
               datasauRus,
               magick,
               kableExtra,
               patchwork)
```

```{r 5126theme, include = FALSE, echo = FALSE, cache = TRUE}
library(tidyverse)
library(janitor)
library(hrbrthemes)
library(ggthemes)

theme_5126 <- function(base_size = 12, base_family = "sans") {
  colors <- deframe(ggthemes::ggthemes_data[["fivethirtyeight"]])
  (theme_foundation(base_size = base_size, base_family = base_family)
  + theme(
      # line = element_line(colour = "black"),
      # rect = element_rect(
      #   fill = colors["white"],
      #   linetype = 0, colour = NA
      # ),
      # text = element_text(colour = colors["Dark Gray"]),
      axis.title = element_blank(),
      # axis.text = element_text(),
      axis.ticks = element_blank(),
      axis.line = element_blank(),
      legend.background = element_rect(),
      legend.position = "bottom",
      legend.direction = "horizontal",
      legend.box = "vertical",
      panel.grid = element_line(colour = NULL),
      panel.grid.major =
        element_line(colour = colors["black"]),
      panel.grid.minor = element_blank(),
      # unfortunately, can't mimic subtitles TODO!
      plot.title = element_text(hjust = 0, size = rel(1.5), face = "bold"),
      plot.margin = unit(c(1, 1, 1, 1), "lines"),
      # strip.background = element_rect(),
      # my updates
      panel.grid.major.x = element_blank(),
      panel.grid.major.y = element_blank(),
      panel.border = element_rect(color = "black",
                                  linewidth = 1,
                                  fill = NA),
      panel.background = element_rect(fill = NA),
      axis.line.x = element_line(color = "gray20",
                                 linewidth = 0.5),
      axis.ticks.x = element_line(color = "gray20",
                                  linewidth = 0.5),
      axis.ticks.y = element_line(color = "gray20",
                                  linewidth = 0.5),
      text = element_text(family = "Roboto Condensed", size = 18),
      axis.text = element_text(size = 18),
      axis.title.y = element_text(family = "Roboto Condensed", face = "bold", size = 18),
      axis.title.x = element_text(family = "Roboto Condensed", face = "bold", size = 18),
      strip.background = element_rect(color = NA,
                                      fill = NA)
  ))
}
```

## Score breakdown

<center>

```{r score-histogram, echo = FALSE, fig.width=6, fig.height = 4}
library(tidyverse)
midterm.df <- c(score = 40,
                34,
                22,
                27,
                44.5,
                37,
                43,
                46,
                35,
                33,
                36,
                48,
                33.5,
                27)

midterm.df %>%
  as_data_frame() %>%
  mutate(score = value) %>%
  ggplot() +
  geom_histogram(mapping = aes(x = score),
                 binwidth = 3,
                 color = "darkred",
                 fill = "tomato") +
  geom_vline(aes(xintercept = 36.7),
             color = "black",
             linewidth = 2) +
  ylab("Count") +
  xlab("Score") +
  theme_5126()
```

</center>

- **Exam average:** 36.7 / 50 = **73.4%**
- **Most missed question:** 7 + **8** (interpreting ANOVA coefficients and plotting residuals)

## Submitting exam corrections

:::box-6-list
By [Friday, March 27th]{.highlight-tomato}, you can submit corrections for all of the questions missed to earn back [half]{.highlight-tomato} of the possible points. 
:::

. . . 

::: indented-text
<i class="fa-solid fa-turn-up fa-rotate-90"></i> For each question, you must not only submit the correct answer, but a detailed explanation of *why* it is the correct answer (i.e., explain what you got wrong in your initial attempt, and why your new answer is correct). 

:::